\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-10-01 doc/USER_MANUAL/manual_SPECFEM3D.tex
small update of the user manual

\end{itemize}
%
\begin{figure}
\noindent \begin{centering}
%%%\includegraphics[width=3in]{figures/gauss_vs_triangle_mod.eps}
\includegraphics[width=3in]{figures/gauss_vs_triangle_mod.pdf}
\par\end{centering}

@@

>>>>

\end{itemize}
%
\begin{figure}
\noindent \begin{centering}
%%%\includegraphics[width=3in]{figures/gauss_vs_triangle_mod.eps}
\includegraphics[width=2.5in]{figures/gauss_vs_triangle_mod.pdf}
\par\end{centering}

@@

\noindent Where  necessary, set  a \texttt{FORCESOLUTION} file  in the
same   way   you    configure   a   \texttt{CMTSOLUTION}   file   with
$N_{\mathrm{sources}}$   entries,  one   for   each  subevent   (i.e.,
concatenate  $N_{\mathrm{sources}}$ \texttt{FORCESOLUTION} files  to a
single   \texttt{FORCESOLUTION}  file).  At   least  one   entry  (not
necessarily the first) must have a  zero time shift, and all the other
entries must have non-negative time  shift. Each subevent can have its
own half latitude, longitude, depth, and force parameters.
